CuO Analysis Details

### 2019-05-20 paper/analysis.tex
finished analysis tex, need to figure out Figures for the outline!

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage[margin=1.0in]{geometry}
\usepackage{lineno}
\linenumbers
\linespread{2}
\renewcommand\linenumberfont{\normalfont\bfseries\small}

@@

\section{Sampling scheme}
In order to do DMD we need to densely sample the low energy space (LES). In our case, we will define the LES as the span of a set of base states. Since we know that our system has a low energy 3d9 and 3d10 sector, we will consider base states with either 9 or 10 electrons in the d-orbitals. Further, in order to consider the effects of a possible Hund's coupling arising in our effective theory from the Cu atom $J_H$, we will need to consider states with both $S_z=1/2, 3/2$. When moving to QMC, we will not be able to consider linear combinations of states with different $S_z$, so in order to sample the effect of $J_H$ densely, we would also like to consider "spin-flip partner" states in the $S_z=1/2$ sector. Consider for example a state Cu3d9\! 4s1 O2p$_{\pi}$3 in the $S_z=1/2$ sector. The half-filled orbitals can have electrons with configuration $up\ up\ dn$ or $up\ dn\ up$, the prior which would have a Hund's descriptor $\frac{1}{2}$ and the latter $-\frac{1}{2}$. Further, we would like to use single determinant Slater-Jastrow wave functions since they have proven to be quite accurate trial wave functions on previous QMC calculations for transition metal oxide molecules [ref]. In order to meet all of these considerations, we chose to collect base states by using spin and spatial-symmetry targeted unrestricted Kohn Sham (UKS) [ref] single determinant states using a B3LYP functional [ref] and Trail-Needs basis with the corresponding pseudopotentials [ref].

First, we generated all the unique base states in the 3d9 and 3d10 sectors using this method. In order to sample the span of the base states we used a shell sampling technique which samples in shells of fixed radius around each of the base states using base state weights of 0.1 - 1.0 in increments of 0.1. Our final set of states in our span were then multiplied by a three-body Jastrow factor, which was optimized on the UKS ground state. Fixed node Diffusion Monte Carlo (FN-DMC) [ref] calculations were run with these states as trial wave functions with a timestep of 0.01 and Tmoves [ref]  in order to get 1-/2-density matrix elements and total energies.

@@

\section{Model selection}
Model selection requires both an understanding of the CuO molecule's low energy excitations and some statistical analysis. We know that the lowest energy excitations of CuO are between the O p and Cu 4s orbitals, as these are the only excitations which allow for a 3d10 configuration. Further, given that we will be including 3d9 states, it's clear that we will need to at least consider the following non-interacting parameters:
$$\bar{\epsilon}_d, \bar{\epsilon}_z, \bar{\epsilon}_\pi, \bar{\epsilon}_s, \bar{t}_\pi, \bar{t}_{d_z^2 z}, \bar{t}_{4s z}, \bar{t}_{dz^2 4s}$$

@@

Since we know that $\bar{n}_d + \bar{n}_z + \bar{n}_\pi + \bar{n}_s = $ Const, we can eliminate $\bar{\epsilon}_d$ from our model since it is linearly dependent on the rest of the parameters. The left over occupation energies are certainly required in our model, given the knowledge we have of our low energy space. Since we know that $U_{4s}$ is required to describe the $4s^2$ states and that the $J_{sd}$ will probably play an important role as well, we just need to do model selection on the four hopping parameters. Figure 2 shows 5-fold cross-validated (CV) linear regressions using \textit{every} model which includes the $\bar{\epsilon}, J_{sd}, U_{4s}$ parameters above and one element in the power set of $\{\bar{t}_\pi, \bar{t}_{d_z^2 z}, \bar{t}_{4s z}, \bar{t}_{dz^2 4s}\}$.

The models are increasing in complexity from left-to-right, and it's clear that the fourth model listed here is as accurate as the most complex model, and significantly simpler. Therefore, we select that model as it captures the most variation with the fewest parameters. The selected model then looks like this: 
$$ \boxed{\text{Selected model: }\bar{\epsilon}_z, \bar{\epsilon}_\pi, \bar{\epsilon}_s, \bar{t}_\pi, J_{sd}, U_{4s}}$$

\section{Model fitting}
We conducted a weighted least squares regression on our samples in order to fit the six parameters in our selected model. The higher density of states with 3d9 occupation made it so that an unweighted linear regression would bias towards a more accurate description of the 3d9 states, leaving the 3d10 states fit very poorly. Since we are particularly interested in describing the lowest energy eigenstates accurately, which are 3d10 in character, we need to weight our linear regression so that the 3d10 sector is fit more accurately than in the unweighted case. The weighting function we used was $e^{-\beta E_{DMC}}$, where $\beta$ is a variable "temperature" which was varied from 0.25 to 3.75 in increments of 0.25. We find that in the range of $\beta \in \{1.5, 2.5\}$ the model does not change very much, therefore we select a model at $\beta = 2.0$, which leads to the following set of regressed parameters:
\begin{multline}
 \boxed{\text{Final model }  (\beta=2): \bar{\epsilon}_z = 1.06(6) eV, \bar{\epsilon}_\pi = 2.12(5) eV, \bar{\epsilon}_s = 3.08(4) eV}\\
\boxed{\bar{t}_\pi = 0.52(4) eV, J_{sd} = -0.5(1) eV, U_{4s} = 3.9(2) eV}
\end{multline}

In order to look at the predictions of this model, we can rotate the MO basis elements into the IAO basis elements. Doing so yields the following more complicated model (note the lack of bars on the model parameters now!):

\begin{multline}
 \boxed{\text{Final model }  (\beta=2): \epsilon_{d_\delta} = 0.00 eV, \epsilon_{d_\pi} = -0.10 eV, \epsilon_{d_z^2} = 0.41 eV }\\
 \boxed{\epsilon_z = 1.2 eV, \epsilon_\pi = 2.21 eV, \epsilon_s = 2.44 eV}\\
\boxed{t_\pi = -0.22 eV, t_{d_z^2 s} = 0.38 eV, t_{s z} = 0.80 eV, t_{d_z^2 z} = 0.70 eV}\\
\boxed{  J_{sd} = -0.5(1) eV, U_{4s} = 3.9(2) eV}
\end{multline}

Shown in Figure 3 are predictions using $\beta = 2.0$ with 95\% confidence intervals on the full set of samples and only on the base states. In both cases the model was fit using the full set of samples. Figure 4 shows for $\beta=2.0$ the sample weights versus the trace ($\bar{n}_{3d} + \bar{n}_{p_z} + \bar{n}_{p_\pi} + \bar{n}_{4s}$) of the 1-rdm in our chosen MO basis for the different samples. As mentioned in section 3, the weights of samples which have a trace that vary significantly from the ground state trace of 14.80 are small, indicating that our regression is fitting primarily to states for which the MO basis is functioning properly.

@@

\pagebreak
%Figure 2
\begin{figure}
\includegraphics[width=1.0\textwidth]{../qwalk/ub3lyp_s1_/analysis/cv_valid.pdf}
\caption{5-fold CV regressions for model selection}
\end{figure}

%Figure 3
\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/fit.pdf}
  \caption{DMC predictions for all samples.}
  \label{fig:sub6}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/fit_baseonly.pdf}
  \caption{DMC predictions for basestates. }
  \label{fig:sub7}
\end{subfigure}
\label{fig:test2}
\caption{DMC regression using all states and $\beta=2.0$.}
\end{figure}

%Figure 4
\begin{figure}
\includegraphics[width=1.0\textwidth]{../qwalk/ub3lyp_s1_/analysis/w_vs_t.pdf}
\caption{Weights versus trace for linear regression with $\beta=2.0$.}
\end{figure}

%Figure 5
\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/beta_dmc_eigenvalues.pdf}
  \caption{Eigenvalues of DMC fit model, hue $\beta$.}
  \label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/beta_dmc_eigenvalues_sz.pdf}
  \caption{Eigenvalues of DMC fit model, hue $S_z$.}
  \label{fig:sub2}
\end{subfigure}
\label{fig:test1}
\caption{Eigenstates of models from DMC}
\end{figure}

%Figure 6
\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/roks_eigenvalues.pdf}
  \caption{Eigenvalues of ROKS effective model.}
  \label{fig:sub3}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/uks_eigenvalues.pdf}
  \caption{Eigenvalues of UKS effective model.}
  \label{fig:sub4}
\end{subfigure}
\label{fig:test2}
\caption{Eigenstates of 1-particle models from DFT}
\end{figure}

%Table
%\begin{wrapfigure}{r}{0.4\textwidth}
%\begin{tabular}{lll}
% &  DMC (eV) & ROKS (eV) \\
%$\epsilon_{d_\delta}$ &  0.00 & 0.00  \\
%$\epsilon_{d_\pi}$ & -0.10 & -0.36 \\
%$\epsilon_{d_{z^2}}$ & 0.41 & 0.52 \\
%$\epsilon_z$ & 1.20 & 0.66 \\
%$\epsilon_\pi$ & 2.21 & 0.85 \\
%$\epsilon_s$ &  2.44 & 4.24 \\
%$t_\pi$ & -0.22 & -1.14 \\
%$t_{s d_{z^2}}$ & 0.38 & 0.97 \\
%$t_{s z}$ & 0.80 & 1.86\\
%$t_{d_{z^2} z}$ & 0.70 & 1.55\\
%$J_{sd}$ & -0.51 & 0.00 \\ 
%$U_s$ & 3.91 & 0.00 \\
%\end{tabular}
%\caption{Parameter differences between DFT/DMC models}
%\end{wrapfigure}
\end{document}

>>>>

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage[margin=1.0in]{geometry}
\usepackage{lineno}
\usepackage{float}

@@

\section{Sampling scheme}
In order to do DMD we need to densely sample the low energy space (LES). In our case, we will define the LES as the span of a set of base states. Since we know that our system has a low energy 3d9 and 3d10 sector, we will consider base states with either 9 or 10 electrons in the d-orbitals. Further, in order to consider the effects of a possible Hund's coupling arising in our effective theory from the Cu atom $J_H$, we will need to consider states with both $S_z=1/2, 3/2$. When moving to QMC, we will not be able to consider linear combinations of states with different $S_z$, so in order to sample the effect of $J_H$ densely, we would also like to consider "spin-flip partner" states in the $S_z=1/2$ sector. Consider for example a state Cu3d9\! 4s1 O2p$_{\pi}$3 in the $S_z=1/2$ sector. The half-filled orbitals can have electrons with configuration $up\ up\ dn$ or $up\ dn\ up$, the prior which would have a Hund's descriptor $\frac{1}{2}$ and the latter $-\frac{1}{2}$. Further, we would like to use single determinant Slater-Jastrow wave functions since they have proven to be quite accurate trial wave functions on previous QMC calculations for transition metal oxide molecules [ref]. In order to meet all of these considerations, we chose to collect base states by using spin and spatial-symmetry targeted unrestricted Kohn Sham (UKS) [ref] single determinant states using a B3LYP functional [ref] and Trail-Needs basis with the corresponding pseudopotentials [ref]. Spin and spatial-symmetry targeted UKS cannot generate the following singly excited states: $(3d_\pi \rightarrow 2p_\pi)|GS\rangle, (3d_{z^2} \rightarrow 2p_\pi)|GS\rangle$. We tried and failed to converge these excited states using constrained DFT. Therefore the span of the basestates we are sampling is not the complete 3d9 and 3d10 sectors of the Hilbert space.

In order to sample the span of the base states we used a shell sampling technique which samples in shells of fixed radius around each of the base states using base state weights of 0.1 - 1.0 in increments of 0.1. Our final set of states in our span were then multiplied by a three-body Jastrow factor, which was optimized on the UKS ground state. Fixed node Diffusion Monte Carlo (FN-DMC) [ref] calculations were run with these states as trial wave functions with a timestep of 0.01 and Tmoves [ref]  in order to get 1-/2-density matrix elements and total energies.

@@

\section{Model selection and fitting}
Model selection requires both an understanding of the CuO molecule's low energy excitations and some statistical analysis. We know that the lowest energy excitations of CuO are between the O p and Cu 4s orbitals, as these are the only excitations which allow for a 3d10 configuration. Further, given that we will be including 3d9 states, it's clear that we will need to at least consider the following non-interacting parameters:
$$\bar{\epsilon}_d, \bar{\epsilon}_z, \bar{\epsilon}_\pi, \bar{\epsilon}_s, \bar{t}_\pi, \bar{t}_{d_z^2 z}, \bar{t}_{4s z}, \bar{t}_{dz^2 4s}$$

@@

Since we know that $\bar{n}_d + \bar{n}_z + \bar{n}_\pi + \bar{n}_s = $ Const, we can eliminate $\bar{\epsilon}_d$ from our model since it is linearly dependent on the rest of the parameters. The left over occupation energies are certainly required in our model, given the knowledge we have of our low energy space. Since we know that $U_{4s}$ is required to describe the $4s^2$ states and that the $J_{sd}$ will probably play an important role as well, we just need to do model selection on the four hopping parameters.

\subsection{Ordinary Linear Regression (OLS)}
To choose a model we first conduct OLS on all sixteen models which have subsets of these hopping parameters and conducting, We then removed from consideration any model which had OLS coefficients which were zero within two standard deviations of the mean, derived from boostrap resampling. We find that the $R^2$ scores between the resultant models are comparable and high, above 0.95. Since we were not able to sample the full low-energy (LE) space, the $R^2$ score itself is not a complete description of the validity of a model our LE space since an increased $R^2$ score can be due to overfitting of the model within our sample space (SS), leading to large extrapolation errors of our model predictions in the unsampled parts of the LE space. In order to investigate the extent of the extrapolation errors between models, we ran exact diagonalization (ED) calculations on our models in the IAO basis. After constructing the means and errors of the eigenvalues by bootstrapping, we removed any models with had an average error in the eigenvalues greater than 0.25 eV. This leaves just five models under consideration which have comparable $R^2$ score and small errors in the ED eigenvalues. Within these five models are two states which have a large extrapolation error as shown in the red boxes of Figure 2. The two states under consideration are a $(3dz^2 \rightarrow 2p_\pi)|GS\rangle, (2p_\pi \rightarrow 4s, d\bar{t}_\pi = 0)|GS\rangle$. As described earlier, the first state was not accessible by our sampling method and therefore no samples within SS can constrain the energy of this state. The latter state is also outside our sample set for a less obvious reason. Our sample space does contain a $(2p_\pi \rightarrow 4s)|GS\rangle$ state, however it has $d\bar{t}_\pi > 0$ because of the bonding nature of the $3d_\pi, 2p_\pi$ orbitals. In order to get the $d\bar{t}_\pi = 0$ state would require there to be no bonding between these orbitals or a linear combination with a state $d\bar{t}_\pi < 0$. Neither of these conditions are possible within our SS, hence the $(2p_\pi \rightarrow 4s, d\bar{t}_\pi = 0)|GS\rangle$ state is not contained in SS. Therefore, in order to pick one model out of our five potential models, we need to apply constraints on states which the ED may describe as low-energy, but which we did not sample.

%Figure 2
\begin{figure}[H]
\centering
\includegraphics[width=0.9\linewidth]{extrap.pdf}
\label{fig:extrap}
\caption{Two out of the five potential models with red boxes indicating the low-energy states which suffer a large extrapolation error.}
\end{figure}

\subsection{OLS with a prior}
In order to constrain samples outside of our set we can use information about eigenstates in LE - SS to construct a Bayesian prior. We know that LE - SS should be spanned by states of type $(3d_\pi \rightarrow 2p_\pi), (3d_{z^2} \rightarrow 2p_\pi), (3d_{z^2} \rightarrow 2s)$ and any composite excitations built on these states. While we cannot generate wave functions which represent these states using UKS, we can generate wave functions with higher energy which lack relevant orbital relaxations via molecular orbital excitations on the UKS ground state. Doing so and using these as trial functions in DMC, we find that all of these states have DMC energies $\geq$ 3.5 eV. This energy provides upper bounds for the lowest energy states with these certain occupation properties, and allows us to construct a pretty reasonable prior.

$$\text{\textbf{Prior: }Any eigenstates outside of our SS should have an energy expectation } \langle H \rangle \sim \langle H_m \rangle \ge E_{cut} = 2 eV$$

The choice of 2eV as our lower bound for these eigenvalues was chosen because it falls significantly below 3.5 eV, allowing for the possibility of these states being heavily relaxed, but also constraining the energy to be higher than the lowest energy singly excited 3d10 states. In order to enforce this prior we use the following cost function to fit our linear models:

$$ \text{Cost} = \sum_i (y_i - \hat{y}_i)^2 + \lambda\sum_p Sig(E_{cut} - E_p), Sig(x) = \frac{1}{1+e^{-x}}.$$

The first term of this cost function is just the standard OLS cost with index $i$ running over our DMC samples within SS. The second term penalizes eigenstates which have energy below the chosen $E_{cut} = 2eV$. The index $p$ here runs over the eigenstates from section 4.1 which had a large extrapolation error. Therefore the second term is a simple implementation of our prior. The value of $\lambda$ can be varied in order to tradeoff the importance of each term.

Starting with our five initial models, we allow $\lambda$ to vary between 0 to 40 with steps of 5 and conduct our linear regression with the above cost fuction. We then pass these models into ED and remove any models which have energy errors greater than 0.25 eV as before. Figure 3 shows the difference between $E_p$ and $E_{cut} = 2eV$ for the two different states composing the index $p$. It is pretty clear that the only model which is best at satisfying the prior for \textit{both} states is model 5. The regression with model 5 and $\lambda = 15$ match our prior the best and still have a good $R^2 = 0.96$ value and small noise. The final chosen model then accurately describes our SS and satisfies our prior for states within LE - SS and has form: 
\begin{multline}
 \boxed{\text{Final model }: \bar{\epsilon}_z = 0.65(7) eV, \bar{\epsilon}_\pi = 1.8(1) eV, \bar{\epsilon}_s = 3.0(1) eV, J_{sd} = -0.8(3) eV, U_{4s} = 3.8(5) eV}
\end{multline}

%Figure 3
\begin{figure}[H]
\centering
\includegraphics[width=0.9\linewidth]{prior.pdf}
\label{fig:extrap}
\caption{Difference from cutoff for different models for different $\lambda$.}
\end{figure}

@@

\end{document}

### 2019-05-20 paper/old_outline.tex
finished analysis tex, need to figure out Figures for the outline!

\documentclass{article}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage[margin=1.0in]{geometry}

@@

\section{Figures}

%Figure 1
\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/fit_0_sel2_log.pdf}
  \caption{Prediction of linear regression on full set of samples.}
  \label{fig:Regression1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/fit_0_sel2_log_base.pdf}
  \caption{Prediction of linear regression on base states only.}
  \label{fig:Regression2}
\end{subfigure}
\label{fig:Regression}
\caption{Linear regression predictions for total energy compared to DMC energies.}
\end{figure}

%Figure 2
\begin{figure}
\centering
\includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/}
\label{fig:Regression}
\caption{Results for energies and 1-/2-body properties of eigenstates from exact diagonalization of our model Hamiltonian.}
\end{figure}

\section{Supplementary Material}

\end{document}

>>>>

\documentclass{article}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage[margin=1.0in]{geometry}
\usepackage{float}

@@

\section{Figures}
%Figure 1
\begin{figure}[H]
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/regr_log.pdf}
  \caption{Prediction of linear regression on full set of samples.}
  \label{fig:Regression1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/regr_log_base.pdf}
  \caption{Prediction of linear regression on base states only.}
  \label{fig:Regression2}
\end{subfigure}
\label{fig:Regression}
\caption{Linear regression predictions for total energy compared to DMC energies.}
\end{figure}

%Figure 2
\begin{figure}[H]
\centering
\includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/ed_0_log.pdf}
\label{fig:ED}
\caption{Results for energies and 1-/2-body properties of eigenstates from exact diagonalization of our model Hamiltonian.}
\end{figure}

\section{Supplementary Material} 
%Supplementary Figure 1
\begin{figure}[H]
\centering
\includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/r2_test.pdf}
\label{fig:OneParm}
\caption{Cross validated R2 scores for all sixteen models under consideration, hued by $\beta$.}
\end{figure}

%Supplementary Figure 2
\begin{figure}[H]
\centering
\includegraphics[width=\linewidth]{../qwalk/ub3lyp_s1_/analysis/Xerr.pdf}
\label{fig:Xerr}
\caption{Ranges of parameters from ED using the first 80 eigenstates compared against the ranges of the DMC training data.}
\end{figure}

%Supplementary Figure 3
\begin{figure}[H]
\centering
\includegraphics[width=0.9\linewidth]{../qwalk/ub3lyp_s1_/analysis/ed_combined_log.pdf}
\label{fig:ED_comp}
\caption{ED results for the four selected models, different models have different markers. Models with more parameter have larger error bars, but all three models have similar results within errorbars.}
\end{figure}

%Table 1
%\begin{figure}[H]
\begin{table}[H]
\centering
\begin{tabular}{l|lllll}
    & Model 0 & Model 2 & Model 3 & Model 8 & Model 14 \\ \hline
$\bar{\epsilon}_s$  & 3.0(1)  & 3.1(1)  & 3.0(1)  & 3.1(1)  & 2.9(1)   \\
$\bar{\epsilon}_\pi$ & 1.9(1)  & 1.7(1)  & 1.9(2)  & 1.4(2)  & 1.4(2)   \\
$\bar{\epsilon}_z$ & 0.8(1)  & 0.6(1)  & 0.8(2)  & 0.4(2)  & 0.6(2)   \\
$\bar{t}_{sz}$& 0       & -0.5(1) & 0       & -0.7(2) & -0.4(2)  \\
$\bar{t}_{sz}$& 0       & 0       & \textcolor{red}{-0.2(5)} & 0.8(4)  & \textcolor{red}{0.4(5)}   \\
$\bar{t}_{ds}$& 0       & 0       & 0       & 0       & 0.7(4)   \\
$\bar{t}_{\pi}$& 0       & 0       & 0       & 0       & 0        \\
$J_{sd}$ & -0.8(3) & -0.5(3) & -0.7(3) & -0.7(3) & -0.6(3)  \\
$U_s$  & 4.7(5)  & 4.2(6)  & 4.7(5)  & 4.0(5)  & 3.7(6)  
\end{tabular}
\label{fig:Table1}
\caption{Model parameters for models with appropriate descriptor ranges.}
\end{table}
%\end{figure} 
\end{document}

### 2019-05-20 paper/outline.tex
finished analysis tex, need to figure out Figures for the outline!

\documentclass{article}
\begin{document}
\section{Introduction}
\begin{enumerate}
\item \textbf{General goal: }
Systematically develop model Hamiltonians which can accurately describe the energies as well as one- and two-particle properties of the lowest lying eigenstates for transition-metal oxide (TMO) molecules.

@@

\item \textbf{State of the art: } Common approaches to building these model Hamiltonians use effective single particle theories like Density Functional Theory (DFT) to generate an effective 1-body model or use the known energy spectrum of the TMO molecules to fit a model with many-body interactions.

\item\textbf{How are we advancing state of the art: } We have systematically developed a many-body model which can accurately describe the energies, one- and two-particle properties of the lowest lying eigenstates for the neutral CuO molecule using \textit{ab-initio} Quantum Monte Carlo (QMC) calculations and a density-matrix downfolding (DMD) procedure. 
\end{enumerate}

\section{Figures}

\end{document}

>>>>

\documentclass{article}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{subcaption}
\usepackage[margin=1.0in]{geometry}
\usepackage{float}

\begin{document}
\section{Introduction}
\begin{enumerate}
\item \textbf{General goal: }
Systematically develop model Hamiltonians which can accurately describe the energies and properties of the lowest lying eigenstates for transition-metal oxide (TMO) molecules.

@@

\item \textbf{State of the art: } Common approaches to building these model Hamiltonians use effective single particle theories like Density Functional Theory (DFT) to generate an effective 1-body model or use the known energy spectrum of the TMO molecules to fit a model with many-body interactions. 
\textcolor{red}{Have to find references for this one, not sure how true this is.}

\item\textbf{How are we advancing state of the art: } We have systematically developed a many-body model which can accurately describe energies and properties of the lowest lying eigenstates for the neutral CuO molecule using \textit{ab-initio} Quantum Monte Carlo (QMC) calculations and a density-matrix downfolding (DMD) procedure. 
\end{enumerate}

%Figure 1 - Show extrapolation error somehow
%Figure 2 - Show prior regression results
%Figure 3 - Show final regression + ED
\end{document}
